Research Cases

### 2025-11-06 Code/R/Research/cases_research.Rmd
Implement fast HOSVD

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

>>>>

## Parameters for P from 2 to 12 with one periodic
```{r}
# P <- 2
# P_case <- "_c2"
# P <- 4
# P_case <- "_c4"
# P <- 8
# P_case <- "_c8"
P <- 12
P_case <- "_c12"

rates.true <- matrix(rep(0, P), nrow = P)
rates_case <- "_nr"

freqs.true <- matrix(rep(0.2, P), nrow = P)
freqs_case <- "_ef"

A <- matrix(rnorm(P), nrow = P)
A_case <- "_da"

phases.true <- matrix(rep(0, P), nrow = P)
phases_case <- "_ep"

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/one_periodic_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/one_periodic", full_case, ".RData"))
}

# if (is.matrix(signal)) {
#   ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
#   tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
#   save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
# } else {
#   ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
#   tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
#   save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
# }
```
